### 2020-07-28 README.Rmd
spelling

`neonstore` provides quick access and persistent storage of NEON data tables. 
`neonstore` emphasizes simplicity and a clean data provenance trail, see 
(Provenance)[/#Provenance].

@@

- `neonstore` aims to provide persistent storage, writing raw data files to
  the appropriate app directory for your operating system (see `rappdirs`,
  [Ratnakumar et al 2016](https://CRAN.R-project.org/package=rappdirs)). 
  More details about this can be found in [Provenance](/#Provenance), below.
- `neon_download()` provides  clean and concise progress bars for the two key
  processes involved: querying the API to obtain download URLs (which involves no 
  large data transfer but counts against API rate limiting, see below), and the
  actual file downloads.
- `neon_download()` will verify the integrity of file downloads against the MD5
  hashes provided. 
- `neon_download()` will omit downloads of any existing data files in the local 
  store.  
- You can request multiple products at once using vector notation, though API
  rate limiting may interfere with large requests.
- `neon_download()` uses `curl::curl_download()` instead of `downloadr` package
  used in `neonUtilities`, which can be finicky on Windows and older versions of R. 
- `neonstore` has slightly lighter dependencies: only `vroom` and `httr`, and
  packages already used by one of those two (`curl`, `openssl`).

>>>>

`neonstore` provides quick access and persistent storage of NEON data tables. 
`neonstore` emphasizes simplicity and a clean data provenance trail, see 
Provenance section below.

@@

- `neonstore` aims to provide persistent storage, writing raw data files to
  the appropriate app directory for your operating system (see `rappdirs`,
  [Ratnakumar et al 2016](https://CRAN.R-project.org/package=rappdirs)). 
  More details about this can be found in Provenance, below.
- `neon_download()` provides  clean and concise progress bars for the two key
  processes involved: querying the API to obtain download URLs (which involves no 
  large data transfer but counts against API rate limiting, see below), and the
  actual file downloads.
- `neon_download()` will verify the integrity of file downloads against the MD5
  hashes provided. 
- `neon_download()` will omit downloads of any existing data files in the local 
  store.  
- You can request multiple products at once using vector notation, though API
  rate limiting may interfere with large requests.
- `neon_download()` uses `curl::curl_download()` instead of `downloadr` package
  used in `neonUtilities`, which can be finicky on Windows and older versions of R. 
- `neonstore` has slightly lighter dependencies: only `vroom` and `httr`, and
  packages already used by one of those two (`curl`, `openssl`).
